Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
Move last table

The same observations are made for the MFCCs for a $k\leq5$. However for a rank $k$ greater than $5$, there is no clear evidence that \emph{ob-c} and \emph{ob-w} approaches improve the results compared to \emph{early}. The latter even outperforms \emph{ob-a} for $k\geq5$.

From this it appears that, although the \emph{ob} approaches are able to better retrieve the similarities between close scenes compared to \emph{early}, they are of no help when considering distant scenes of the same class. This may be due to the fact that, at some point, the MFCCs fail to dissociate the discriminative events of a scene from the non-informative ones, thus making a centroid-based description useless, or even counterproductive when the centroids are not weighted/selected.

@@

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to separately characterize distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.
Surprisingly, although we ran an extensive number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in temporal integration, namely majority voting. Among object-based methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm0.7$.

%\ml{explain why ?}

@@

Representing a scene using a reduced set of representatives, with adapted similarity strategies allows us to improve ASSR performance compared to the BOF approaches based on GMMs. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- is represented using a convolutional network such as the scattering transform, while larger time scales -- \ie over a second -- are modeled as adaptive aggregates.

>>>>

The same observations are made for the MFCCs for $k\leq5$. However for a rank $k$ greater than $5$, there is no clear evidence that \emph{ob-c} and \emph{ob-w} approaches improve the results compared to \emph{early}. The latter even outperforms \emph{ob-a} for $k\geq5$. From this it appears that, although the \emph{ob} approaches are able to better retrieve the similarities between close scenes compared to \emph{early}, they are of no help when considering distant scenes of the same class. This may be due to the fact that, at some point, the MFCCs fail to dissociate the discriminative events of a scene from the non-informative ones, thus making a centroid-based description useless, or even counterproductive when the centroids are not weighted/selected.

@@

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to separately characterize distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.

Surprisingly, although we ran a large number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none managed to outperform the baseline strategy in temporal integration, namely majority voting. Among object-based methods, the best result is achieved by the \emph{ob-c} approach with log-compressed scattering coefficients, reaching an accuracy of $66\% \pm0.7$. This might be due to the fact that the discriminability gained by the object-based approach is already gained by the classifiers during the training and the fact the object-based approach is equivalent to an early fusion approach, which in the case of the DCASE 2013 has not been identified as beneficial due to the dataset size (see discussion in Section \ref{sec:eili}).

@@

Representing a scene using a reduced set of representatives, with adapted similarity strategies, allows us to improve ASSR performance compared to the BOF approaches based on GMMs which have been demonstrated to be equivalent to early integrations scheme on well-balanced datasets \cite{lagrange:hal-01082501}. These results advocate for a hierarchical model of the scene, where short-time structure -- \ie below a second -- is represented using a convolutional network such as the scattering transform, whereas larger time scales -- \ie over a second -- are modeled as adaptive aggregates.
